\documentclass[../thesis.tex]{subfiles}

\begin{document}
\chapter*{Acknowledgement}

First and foremost, I would like to thank my honour thesis supervisor Weidong Xiao who generously provided resources, insights, and feedback throughout the honour year to help me improve the design continuously. He shared his vision during the initial meeting and I am glad that we have the same interest in developing such a communication system.

Doctor Wibowo Hardjawana is a supervisor that is responsible for telecommunication. He offered valuable recommendations on the selection of microcontrollers and provided a short lecture on cool their work is (and how expensive the equipment are). I am very grateful for his help that I can find a microcontroller that works well with the project straight away.

The research student Qiyang Lei who is responsible for creating the data measuring and charging side of the system is a master at frying expensive electrical components. He offered many bits of help in understanding how the experimental setup works, and the testing in this thesis cannot be completed without his hard work at measuring, charging, and frying the experimental setup.

I want to thank the research student Ye Chen and Xiaozhou Liu, who is incredibly helpful at helping me and Qiyang solving electrical issues that we do not understand the reason why it happened. It is also worth mentioning that Ye Chen had provided a generous amount of jokes to keep the mood upbeat.

\end{document}